Stable Neo-Hookean Flesh Simulation

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
finally term finished, except hessian

with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use we write $\frac{\partial J}{\partial F}$ as cross products:
\[
\frac{\partial J}{\partial F} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
\]

@@

\textbf{Gradient}:
\begin{align*}
\mathbb{G}(\mathbf{F}) &= \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial fi} \\ \\
\operatorname{vec}(\mathbb{G}(\mathbf{F})) &= \mathbf{\check{G}} = \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right) \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right)^\intercal = \mathbf{\check{g}} \mathbf{\check{g}}^\intercal
\end{align*}

@@

\todoredefined[inline]{
TODO: Make notation consistent (bold, cursive etc.) Explain better each step. Include all calculations? Make matrix of matrices more beautiful (more space). Eigenvalues of Mu term?
}

>>>>

with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use we write $\frac{\partial J}{\partial \mathbf{F}}$ as cross products:
\begin{equation}\label{eq:cross_product}
\frac{\partial J}{\partial \mathbf{F}} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
\end{equation}

@@

\textbf{Gradient}: The gradient term also has the same structure as the two terms before with different entries defined by
\[
\mathbb{G}(\mathbf{F}) = \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial fi}.
\]
The vectorized matrix $\mathbf{\check{G}}$ can be written in a similar form as for the Mu term. With the help of the cross product of $\partial J / \partial \mathbf{F}$ stated in eq. \ref{eq:cross_product} $\mathbf{\check{G}}$ can be written as an outer product in the following way:
\[
\operatorname{vec}(\mathbb{G}(\mathbf{F})) = \mathbf{\check{G}} = \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right) \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right)^\intercal = \mathbf{\check{g}} \mathbf{\check{g}}^\intercal.
\]
As in the Mu term one can notice a single non-zero, non-negative:
\[
\| \mathbf{\check{g}} \|^2_2 = \left\| \frac{\partial J}{\partial \mathbf{F}} \right \|^2_F = \left[ (\sigma_0 \sigma_1)^2 + (\sigma_0 \sigma_2)^2 + (\sigma_1 \sigma_2)^2 \right].
\]
The eigenvector is $\mathbf{\check{g}} / \| \mathbf{\check{g}} \|$.

@@

\todoredefined[inline]{
TODO: Make notation consistent (bold, cursive etc.) Explain better each step. Include all calculations? Make matrix of matrices more beautiful (more space). Eigenvalues of Mu and Gradient term better explain?
}
